Variable creation ObjectInAction

### 2019-04-01 Final Manuscript.Rmd
more testing!
Adding alphas to manuscript, fixing manuscript data file, other stuff!!

```{r setup, include = FALSE}
library("papaja")
```

@@

```{r, include=FALSE}
x <- 7
```

hi I'm the number `r x`.

@@

## Participants

>>>>

```{r setup, include = FALSE}
library("papaja")
library(nlme)
library(haven)
library(devtools)
library(psych)
library(mosaic)
library(tidyr)
library(dplyr)
library(irr)

clark_measures <- read_spss("Raw data/Clark College Relationships Data/College_Relationship_Measures_1.sav")
smith <- read_spss("Raw data/Smith College Relationships Data/College_Relationship_Dyadic_September_14_2018_12_17.sav")
```

@@

```{r, include=FALSE}
#######Alphas

###SOO

#Clark
#SOO
clark_extsoo_alpha <- psych::alpha(select(clark_measures, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10))$total[2]
clark_intsoo_alpha <- psych::alpha(select(clark_measures, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12))
#Smith
smith_extsoo_alpha <- psych::alpha(select(smith, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10))$total[2]
smith_intsoo_alpha <- psych::alpha(select(smith, otherint_3, otherint_4, otherint_7, otherint_8, otherint_9, otherint_11, otherint_12))$total[2]

##Interaction Authenticity
#Clark
clark_intauth_alpha <- psych::alpha(select(clark_measures, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_5, interaux_6))$total[2]
#Smith
smith_intauth_alpha <- psych::alpha(select(smith, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_5, interaux_6))$total[2]

##SSO
#Clark
clark_howbody_alpha <- psych::alpha(select(clark_measures, howbody_1, howbody_2))$total[2]
#Smith
smith_howbody_alpha <- psych::alpha(select(smith, howbody_1, howbody_2))$total[2]

##Relationship Agency
#Clark
clark_relag_alpha <- psych::alpha(select(clark_measures, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9))$total[2]
smith_relag_alpha <- psych::alpha(select(smith, relag_1, relag_2, relag_3, relag_4, relag_5, relag_6, relag_7, relag_8, relag_9))$total[2]

##Career Aspirations
#Clark
clark_measures <- clark_measures %>% #reverse code certain career aspiration variables
  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))

clark_careerasp_alpha <- psych::alpha(select(clark_measures, careerasp_1, careerasp_2, careerasp_3, careerasp4.r, careerasp_5, careerasp_6, careerasp7.r, careerasp_8, careerasp_9, careerasp10.r))$total[2]

#Smith
smith <- smith %>% #reverse code certain career aspiration variables
  mutate(careerasp4.r = (min(careerasp_4, na.rm = TRUE) + max(careerasp_4, na.rm = TRUE) - careerasp_4),
         careerasp7.r = (min(careerasp_7, na.rm = TRUE) + max(careerasp_7, na.rm = TRUE) - careerasp_7),
         careerasp10.r = (min(careerasp_10, na.rm = TRUE) + max(careerasp_10, na.rm = TRUE) - careerasp_10))

smith_careerasp_alpha <- psych::alpha(select(smith, careerasp_1, careerasp_2, careerasp_3, careerasp4.r, careerasp_5, careerasp_6, careerasp7.r, careerasp_8, careerasp_9, careerasp10.r))$total[2]

###TSO
#Clark--external and internal
clark_funcTSO_alpha <- psych::alpha(select(clark_measures,tso_1, tso_2, tso_4, tso_7, tso_9))$total[2]
clark_physTSO_alpha <- psych::alpha(select(clark_measures,tso_3, tso_5, tso_6, tso_8, tso_10))$total[2]
#Smith--external and internal
smith_funcTSO_alpha <- psych::alpha(select(smith,tso_1, tso_2, tso_4, tso_7, tso_9))$total[2]
smith_physTSO_alpha <- psych::alpha(select(smith,tso_3, tso_5, tso_6, tso_8, tso_10))$total[2]
```

@@

## Participants
The data collected in this study sought to replicate Garcia et al. (2016), which sought to measure objectification in previously unacquainted male-female pairs. This data was given to us by Dr. Garcia, who collected data from both Smith College and Clark University. The data was ultimately merged and filtered to only include only self-identified female same-sex pairs from both schools. The two samples are often referred to below as Sample 1 (data from Clark University) and Sample 2 (data from Smith College). These participants were mostly first-year college students, with an average age of 18.85 years (SD=1.04). The sample was 48% White/European American, 9% Black/African-American, 28% Asian/Pacific Islander, 9% Latinx, and 5% mixed-race. There were eight White/White pairs and four same race racial minority pairs, for a total of twelve same-race pairs. The remaining twenty were mixed race pairs, of which fifteen were White/racial minority pairings and five were cross-racial minority group pairs. 64% of the sample identified as heterosexual, and 23% identified as gay, lesbian or bisexual. The data is organized in a pairwise fashion such that each row corresponds to one participant in the study, and includes data for themselves and their partner. We would want to generalize these findings to general interactions between women.

### 2019-04-01 Variable creation.Rmd
Adding alphas to manuscript, fixing manuscript data file, other stuff!!

Clark Scale Scores--creating scale scores for the Clark data.
```{r}
#Social Physique Anxiety
clark_measures <- clark_measures %>%
  #reverse code physical anxiety variable
  mutate(physanx5.r = (min(physanx_5, na.rm = TRUE) + max(physanx_5, na.rm = TRUE) - physanx_5),
         #get average for scale score
         physanx = (physanx_1 +physanx_2 +physanx_3+physanx_4+physanx5.r+physanx_6)/6)

#SOO -- subtract internal SOO from external SOO
clark_measures$extSOO <- rowMeans(dplyr::select(clark_measures, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10), na.rm=TRUE) #get average

@@

clark_measures$TSO <- clark_measures$physTSO - clark_measures$funcTSO
clark_measures$TSO <- clark_measures$TSO*(-1)

#satisfaction--reverse code negative variables and then average with the rest
clark_measures <- clark_measures %>%
  mutate(anxious.r = (min(inter_2, na.rm = TRUE) + max(inter_2, na.rm = TRUE) - inter_2)) %>%
  mutate(uncomfort.r = (min(inter_4, na.rm = TRUE) + max(inter_4, na.rm = TRUE) - inter_4)) %>%
  mutate(hostile.r = (min(inter_8, na.rm = TRUE) + max(inter_8, na.rm = TRUE) - inter_8)) %>%
  mutate(apprehen.r = (min(inter_11, na.rm = TRUE) + max(inter_11, na.rm = TRUE) - inter_11)) %>%
  mutate(aggressive.r = (min(inter_13, na.rm = TRUE) + max(inter_13, na.rm = TRUE) - inter_13))

clark_measures$satisfaction <- rowMeans(select(clark_measures, anxious.r, uncomfort.r, hostile.r, apprehen.r, aggressive.r, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_6), na.rm=TRUE)
```

@@

#Social Physique Anxiety
smith <- smith %>%
  mutate(physanx5.r = (min(physanx_5, na.rm = TRUE) + max(physanx_5, na.rm = TRUE) - physanx_5),
         physanx = (physanx_1 +physanx_2 +physanx_3+physanx_4+physanx5.r+physanx_6)/6) #reverse code physical anxiety variable

@@

smith$TSO <- smith$physTSO-smith$funcTSO
smith$TSO <- smith$TSO*-1

#satisfaction--reverse code negative variables and then average with the rest
smith <- smith %>%
  mutate(anxious.r = (min(inter_2, na.rm = TRUE) + max(inter_2, na.rm = TRUE) - inter_2)) %>%
  mutate(uncomfort.r = (min(inter_4, na.rm = TRUE) + max(inter_4, na.rm = TRUE) - inter_4)) %>%
  mutate(hostile.r = (min(inter_8, na.rm = TRUE) + max(inter_8, na.rm = TRUE) - inter_8)) %>%
  mutate(apprehen.r = (min(inter_11, na.rm = TRUE) + max(inter_11, na.rm = TRUE) - inter_11)) %>%
  mutate(aggressive.r = (min(inter_13, na.rm = TRUE) + max(inter_13, na.rm = TRUE) - inter_13))

smith$satisfaction <- rowMeans(select(smith, anxious.r, uncomfort.r, hostile.r, apprehen.r, aggressive.r, inter_1, inter_3, inter_5, inter_6, inter_7, inter_9, inter_10, interaux_6), na.rm=TRUE)
```

@@

#Read in graded trigram file
smith_trigrams_graded <- read.csv("Smith College Relationships Data/trigrams_graded.csv")

>>>>

Clark Scale Scores--creating scale scores for the Clark data.
```{r}
#SOO -- subtract internal SOO from external SOO
clark_measures$extSOO <- rowMeans(dplyr::select(clark_measures, otherint_1, otherint_2, otherint_5, otherint_6, otherint_10), na.rm=TRUE) #get average

@@

clark_measures$TSO <- clark_measures$physTSO - clark_measures$funcTSO
clark_measures$TSO <- clark_measures$TSO*(-1)
```

@@

@@

smith$TSO <- smith$physTSO-smith$funcTSO
smith$TSO <- smith$TSO*-1
```

@@

#Read in graded trigram file
smith_trigrams_graded <- read.csv("Raw data/Smith College Relationships Data/trigrams_graded.csv")
